Forecasting the United States 2024 Presidential Election Using State as Fixed Effect Through a Bayesain Approach

### 2024-11-04 paper/paper.qmd

Data was analyzed through the R programming software [@citeR] and packages such as tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr], and dplyr [@dplyr] were used to help download, clean, simulate, analyze, and test the data. For model construction and analysis, the following packages were used: rstanarm [@rstanarm1, @rstanarm2], brms [@brms1, @brms2, @brms3], and bayesplot [@bayesplot1, @bayesplot2]

@@

This table displays each candidate's chance of winning and the average number of Elector Votes they received over the 1000 simulated elections. Our model predicts that Harris has a 67.4% chance of winning the US presidential election. While Trump only has a 31.7% chance of winning. There is also a 0.9% chance of a tie On average across the 1,000 simulations Harris wins 279.33 Electoral Votes, while Trump wins on average 258.67 votes.

```{r}
#| label: table-2
#| fig-cap: Election Prediction Results
#| echo: false
#| warning: false
#| message: false

@@

# Load the knitr package
library(knitr)

>>>>

Data was analyzed through the R programming software [@citeR] and packages such as `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `knitr` [@knitr], and `dplyr` [@dplyr] were used to help download, clean, simulate, analyze, and test the data. For model construction and analysis, the following packages were used: `rstanarm` [@rstanarm1; @rstanarm2], `brms` [@brms1; @brms2; @brms3], and `bayesplot` [@bayesplot1; @bayesplot2].

@@

This table displays each candidate's chance of winning and the average number of Elector Votes they received over the 1000 simulated elections. Our model predicts that Harris has a 67.4% chance of winning the US presidential election. While Trump only has a 31.7% chance of winning. There is also a 0.9% chance of a tie On average across the 1,000 simulations Harris wins 279.33 Electoral Votes, while Trump wins on average 258.67 votes.
@fig-predic displays each candidate's chance of winning and the average number of Elector Votes they received over the 1000 simulated elections. Our model predicts that Harris has a 67.4% chance of winning the US presidential election. While Trump only has a 31.7% chance of winning. There is also a 0.9% chance of a tie On average across the 1,000 simulations Harris wins 279.33 Electoral Votes, while Trump wins on average 258.67 votes.

```{r}
#| label: fig-predic
#| fig-cap: Election Prediction Results
#| echo: false
#| warning: false
#| message: false

@@
